SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-24 docs/questioning.tex
more ammendments on the rest of the paper

\section{Dimensions of Study}

In what follows we evaluate published research in attack detection
mechanism based on the following:
\begin{itemize}
\item \textbf{Sensitivity, Specificity}: Reporting of values for True
  Positives ($a$), False Positives ($b$), False Negatives ($c$), True
  Negatives ($d$), on test environments.
\item \textbf{\textsc{ppv}, \textsc{npv}}: Reporting of values for True
  Positives ($A$), False Positives ($B$), False Negatives ($C$), True
  Negatives ($D$), on the performance of the mechanism on environments
  with real attack profiles. Alternatively, since from
  equations~\ref{eq:ppv-se-sp} and~\ref{eq:npv-se-sp} \textsc{ppv}
  and \textsc{npv} can be calculated by the sensitity and specifity
  given the prevalence, reporting of prevalance, sensitivity,
  specificity.
\end{itemize}

@@

Training techniques are based on the ideas of Denning's original
intrusion detection framework~\cite{Den87}.
In particular, a training mechanism,
registers all valid legitimate code statements
during a training phase, most of the time in the form of signatures.
This can be done in various ways according to the implementation.
Then, only those will be accepted, approved or recognized during
production.

@@

>>>>

@@

Training techniques are based on the ideas of Denning's original
intrusion detection framework~\cite{Den87}. In particular, a training
mechanism registers all valid legitimate code statements during a
training phase, most of the time in the form of signatures. This can
be done in various ways according to the implementation. Then, only
those will be accepted, approved or recognized during production.

@@

\section{Analysis Dimensions}

\subsection{Diagnostic Performance}

If published research does not include figures for Sensitivity and
Specificity or values for ($a$)--($d$), on test environments, then it
is not possible to judge the accuracy of the research at all. Even if
we do have such figures, a good research tool is not necessarily a
good practical tool. Even if a research tool scores well on
Sensitivity and Specificity, it may not be very useful in the real
world if the prevalence of the caught attacks is so low that a
positive test result is not likely to indicate a real attack.

To sum up, we evaluate diagnostic performance on two criteria:

\begin{itemize}
\item Reporting of Sensitivity and Specifity, either directly, or
  indirectly from published values of $a$--$d$.
\item Reporting of \textsc{ppv} and \textsc{npv}. This can be direct
  reporting of their values, or indirect from published values of
  $A$--$D$. Also, since from equations~\ref{eq:ppv-se-sp}
  and~\ref{eq:npv-se-sp} \textsc{ppv} and \textsc{npv} can be
  calculated by the sensitity and specifity given the prevalence, it
  can be via reporting prevalance, sensitivity, specificity.
\end{itemize}

\subsection{Computational Performance}

\subsection{Ease of Use}

\subsection{Availability}
